%-------------------------
% Resume in Latex
% Author : Anthony Bird
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large Anthony S Bird} \\ \vspace{5pt}
    \small \faPhone* \texttt{(252)-626-7763} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{birdas273@gmail.com} \hspace{1pt}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Researcher}{Aug. 2021 -- Present}
      {Appalachian State University}{Boone, NC}
      \resumeItemListStart
        \resumeItem{Through creating interpretable convolutional neural networks we use an autoencoder structure to convert current architectural designs into modular designs in order to \textbf{drastically reduce labor and design costs}.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Research Assistant}{Sep. 2019 -- May 2021}
      {Appalachian State University}{Boone, NC}
      \resumeItemListStart
        \resumeItem{Through optimizing classification results on a minimal data-set, \textbf{achieved an accuracy of 91\% compared to the previous 70\%}. This was achieved through bootstrapping, image generation, and data augmentation.}
      \resumeItemListEnd
      
    \resumeSubheading
        {University Tutor}{Jan. 2020 -- May 2021}
        {Appalachian State University}{Boone, NC}
        \resumeItemListStart
          \resumeItem{Tutored fellow students in \textbf{computer science, advanced mathematics, and introductory logic}.}
          \resumeItem{Co-led a drop-in computer science seminar 3 times a week.}
          \resumeItem{Refined knowledge in computer science and math through repeated tutoring and assisting.}
        \resumeItemListEnd
        
      
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Appalachian State University}{Expected December 2022}
      {Master of Computer Science (Concentration in Theoretics)   GPA: 3.87}{Boone, NC}
        \resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Operating Systems,  Machine Learning, Theoretical Computer Science}
        \resumeItemListEnd
        
        
    \resumeSubheading
      {Appalachian State University}{Graduated May 2021}
      {Bachelor of Science in Mathematics}{Boone, NC}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Proofs, Real Analysis, Modern Algebra, Abstract Algebra, Combinatorics, Cryptography and Coding Theory}
        \resumeItemListEnd
        
        
    \resumeSubheading
      {Appalachian State University}{Graduated May 2021}
      {Bachelor of Science in Computer Science}{Boone, NC}
      	
  
 
        
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
        \begin{comment}
        \resumeProjectHeading
          {\textbf{Ellucian Banner System Vulnerability}}{Apr. 2021}
          \resumeItemListStart
            \resumeItem{Ellucian Banner is a secure online system that supplies university students across the country with access to registration, academic, financial, and other personal records maintained by a university.}
            \resumeItem{By reverse engineering the API and decrypting magnetic card stripes, a colleague and I discovered a vulnerability that would allow an attacker to create a copy of any university personnel's or student's magnetic stripe ID card from scratch, without access to the original.}
            \resumeItem{This allowed access to personal information, registration, finances, and dormitories. The issue was responsibly disclosed to the school in order to prevent future unauthorized access to the system. }
        \resumeItemListEnd
        \end{comment}   
        
        \resumeProjectHeading
          {\textbf{Real-time Rich Closed Captioning}} {Jan. 2021 -- In Progress}
          \resumeItemListStart
            \resumeItem{A python based project that creates hypertext rich captions for video and audio.}
            \resumeItem{Able to recognize the most relevant words in a sentence through analysis of n-gram frequency.}
            \resumeItem{Able to define important words to the user in order to make sure they understand the subjects of conversation in real time.}
            \resumeItem{Uses hyper-text references to link to a page containing more information on important words.}
            \resumeItem{Used to caption a live Zoom session class for future archival in Spring of 2021. 
            }
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages} {: Python, Java, C/C++, x86 Assembly, HTML/CSS, SQL, Matlab}\vspace{2pt} \\
     \textbf{Tools}     {: Google Analytics, Git/GitHub, Scrum, Agile, XP, Tensorflow, Keras, PyTorch, NLTK, Scikit-learn, Matplotlib, Tableau}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
